Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-11 review_article.Rmd
figure and section labelling

<!-- Structure of the paper -->
The paper is organised as follows.  The next section describes the choropleth map which is the common approach to disease maps. Section \ref{public} surveys atlases in use today. The (#alternative) describes an alternative display, the cartogram what may be useful for countries that have heterogeneously sized geographic units. The pros and cons of these approaches is discussed in Section [Comparison of mapping methods](#compare). Disease maps are more useful when made interactive, and common options are described in Section [Animation and Interactivity](#interacting), along with a discussion of benefits and disadvantages. The last section summarises the paper and discusses future directions.

@@

```{r supp-grid-create, fig.cap = "Interactive controls of displays in public facing choropleth cancer maps. [a. Globocan 2018: Cancer Today](http://globocan.iarc.fr/Pages/Map.aspx)(Controls for indicator, sex, age groups, continents, and cancer types) , [b. Bowel Cancer Australia Atlas](http://www.bowelcanceratlas.org/) (Controls for indicator, age, year, and geographical areas), [c. The Cancer Atlas ](http://canceratlas.cancer.org/data/#?view=map&metric=INCID_ALL_M) (Controls for predetermined combinations of cancer type or risk factors, mortality or incidence, and gender) [d. Global Cancer Map](http://globalcancermap.com/) (Controls for indicator, and cancer type), [e. United States Cancer Statistics: Data Visualizations](https://gis.cdc.gov/Cancer/USCS/DataViz.html) (Controls for demographics, trends, geography, indicators, risk factors, sex, cancer type, and year)."}
i1 <- png::readPNG('cancer_map_images/interactivity/3.interactivity.png')
i2 <- png::readPNG('cancer_map_images/interactivity/15.interactivity.png')
i3 <- png::readPNG('cancer_map_images/interactivity/4.interactivity.png')
i4 <- png::readPNG('cancer_map_images/interactivity/5.interactivity.png')
i5 <- png::readPNG('cancer_map_images/interactivity/7.interactivity.png')

ggdraw() +
  draw_plot(rasterGrob(i1), 0,  0.13,   .28,  .83) + #a
  draw_plot(rasterGrob(i2), 0.32, 0.56, .68, .4) + #b
  draw_plot(rasterGrob(i3), 0.32, 0.41, .68, .13) + #c
  draw_plot(rasterGrob(i4), 0.32, 0.14, .68, .25) + #d
  draw_plot(rasterGrob(i5), 0, 0, 1, .13) + #e
  draw_plot_label(c("a", "b", "c", "d", "e"), 
    c(0.01, 0.3, 0.3, 0.3, 0.01), 
    c(0.99, 0.99, 0.59, 0.40, 0.19), size = 15)

@@

### Statistical uncertainty
The additional statistics often include a measure of the statistical uncertainty of the values of the statistics presented in a choropleth.
In the review of atlases in the public domain, atlases were considered to report uncertainty to the non-expert user if they included a measure of statistical uncertainty either within or alongside the map [@@roberts2019communication]. 
The maps considered used standard and well known measures including credible intervals and standard deviation, statistical significance, box plots and distributions. Other methods involve providing adjacent maps or overlapping maps with symbols [@VSSDCUC].
The maps employing uncertainty ranged from static pdfs or infographics, to interactive online resources. Communicating the uncertainty associated with the estimates through a confidence (CI) interval, statistical significance levels, boxplots, distribution plots, and reporting sample size and standard deviations.
Close to half of the atlases identified (42%, n=14) included some measure of uncertainty. The most common measure used to represent uncertainty were credible or confidence intervals (CIs).

>>>>

<!-- Structure of the paper -->
The paper is organised as follows.  The next section describes the choropleth map which is the common approach to disease maps. Section XXX surveys atlases in use today. Section XXX describes an alternative display, the cartogram what may be useful for countries that have heterogeneously sized geographic units. The pros and cons of these approaches is discussed in Section  XXX. Disease maps are more useful when made interactive, and common options are described in Section  XXX, along with a discussion of benefits and disadvantages. The last section summarises the paper and discusses future directions.

@@

```{r supp-grid-create, fig.cap = "Interactive controls of displays in public facing choropleth cancer maps. [a. Globocan 2018: Cancer Today](http://globocan.iarc.fr/Pages/Map.aspx)(Controls for indicator, sex, age groups, continents, and cancer types) , [b. Bowel Cancer Australia Atlas](http://www.bowelcanceratlas.org/) (Controls for indicator, age, year, and geographical areas), [c. The Cancer Atlas ](http://canceratlas.cancer.org/data/#?view=map&metric=INCID_ALL_M) (Controls for predetermined combinations of cancer type or risk factors, mortality or incidence, and gender) [d. Global Cancer Map](http://globalcancermap.com/) (Controls for indicator, and cancer type), [e. United States Cancer Statistics: Data Visualizations](https://gis.cdc.gov/Cancer/USCS/DataViz.html) (Controls for demographics, trends, geography, indicators, risk factors, sex, cancer type, and year)."}
i1 <- png::readPNG('cancer_map_images/interactivity/3.interactivity.png') # b in choro grid
i2 <- png::readPNG('cancer_map_images/interactivity/15.interactivity.png') # d in choro grid
i3 <- png::readPNG('cancer_map_images/interactivity/4.interactivity.png')
i4 <- png::readPNG('cancer_map_images/interactivity/5.interactivity.png')
i5 <- png::readPNG('cancer_map_images/interactivity/7.interactivity.png') # e in choro grid

ggdraw() +
  draw_plot(rasterGrob(i1), 0,  0.13,   .28,  .83) + #a
  draw_plot(rasterGrob(i2), 0.32, 0.56, .68, .4) + #b
  draw_plot(rasterGrob(i3), 0.32, 0.41, .68, .13) + #c
  draw_plot(rasterGrob(i4), 0.32, 0.14, .68, .25) + #d
  draw_plot(rasterGrob(i5), 0, 0, 1, .13) + #e
  draw_plot_label(c("i", "ii", "iii", "iv", "v"), 
    c(0.01, 0.3, 0.3, 0.3, 0.01), 
    c(0.99, 0.99, 0.57, 0.40, 0.15), size = 15)

@@

### Statistical uncertainty
The additional statistics often include a measure of the statistical uncertainty of the values of the statistics presented in a choropleth.
In the review of atlases in the public domain, atlases were considered to report uncertainty to the non-expert user if they included a measure of statistical uncertainty either within or alongside the map [@roberts2019communication]. 
The maps considered used standard and well known measures including credible intervals and standard deviation, statistical significance, box plots and distributions. Other methods involve providing adjacent maps or overlapping maps with symbols [@VSSDCUC].
The maps employing uncertainty ranged from static pdfs or infographics, to interactive online resources. Communicating the uncertainty associated with the estimates through a confidence (CI) interval, statistical significance levels, boxplots, distribution plots, and reporting sample size and standard deviations.
Close to half of the atlases identified (42%, n=14) included some measure of uncertainty. The most common measure used to represent uncertainty were credible or confidence intervals (CIs).
